Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-19 talk/vmil2012/paper.tex
write a bit more about guards and bridges

As explained in previous sections, when a specific guard has failed often enogh
a new trace, refered to as bridge, starting from this guard is recorded and
compile. The goal for the execution of bridges, that become a part of the
common path is to favor the performance while staying on the compiled trace.
This means we want wo avoid switching back and forth to the frontend when a
guard corresponding to the bridge fails before we can execute the brigde.
Instead we want to have as little as possible overhead when switching from the
loop path to the bridge.

The process of compiling a bridge is very similar to compiling a loop,
instructions and guards are processed in the same way as described above. The
main difference is the setup phase, when compiling a trace we start with a
clean slate, whilst the compilation of a bridge starts with state as it was
when compiling the guard. To restore the state needed compile the bridge we use
the encoded representation created for the guard to rebuild the bindings from
IR-variables to stack locations and registers used in the register allocator.

Once the bridge has been compiled the trampoline method stub is redirected to
the code of the bridge. In future if the guard fails again it jumps to the
trampoline and then jumps to the code compiled for the bridge, having alsmos no
overhead compared to the execution of the original trace, behaving mainly as
two paths in a conditional block.

>>>>

As explained in previous sections, when a specific guard has failed often enogh
a new trace, refered to as bridge, starting from this guard is recorded and
compiled. When compiling bridges the goal is that future failures of the guards
that led to the compilation of the bridge should execute the bridge without
additional overhead, in particular it the failure of the guard should not lead
to leaving the compiled code prior to execution the code of the bridge.

The process of compiling a bridge is very similar to compiling a loop,
instructions and guards are processed in the same way as described above. The
main difference is the setup phase, when compiling a trace we start with a lean
slate. The compilation of a bridge is starts from a state (register and stack
bindings) that corresponds to the state during the compilation of the original
guard. To restore the state needed compile the bridge we use the encoded
representation created for the guard to rebuild the bindings from IR-variables
to stack locations and registers used in the register allocator.  With this
reconstruction all bindings are restored to the state as they were in the
original loop up to the guard.

Once the bridge has been compiled the trampoline method stub is redirected to
the code of the bridge. In future if the guard fails again it jumps to the code
compiled for the bridge instead of bailing out. Once the guard has been
compiled and attached to the loop the guard becomes just a point where
control-flow can split. The loop after the guard and the bridge are just
condional paths.
